An Adolescent Mini-Neptune in the Kepler Field

### 2021-06-15 paper/ms.tex
minor

For instance, the ``mini-Neptune'' planets, thought to be made of
rocky cores and extended atmospheric envelopes of hydrogen and helium,
are expected to shrink in size by factors of several over their first
$10^8$ years \citep{owen_constraining_2020}.  Specifically, they start
with sizes of 4--12\,$R_\oplus$ at the time of disk dispersal
($\approx$$10^7$\,years), and shrink to sizes of 2--4\,$R_\oplus$ by
10$^8$ years.  This change is driven by a combination of stellar
irradiation and internal heat that powers an outflow, which eventually
depletes or entirely strips the envelope from the rocky core
\citep{Owen_Wu_2013,gupta_sculpting_2019}.  Discovering young planets
and measuring their compositions and atmospheric outflows are key
steps toward testing this paradigm, which is often invoked to explain
the observed radius distribution of both mature exoplanets
\citep{Fulton_et_al_2017}, as well as younger planets
\citep{bouma_cluster_2020}.

>>>>

For instance, the ``mini-Neptune'' planets, thought to be made of
molten rocky cores and extended atmospheric envelopes of hydrogen and
helium, are expected to shrink in size by factors of several over
their first $10^8$ years \citep{owen_constraining_2020}.
Specifically, they start with sizes of 4--12\,$R_\oplus$ at the time
of disk dispersal ($\approx$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  This change is driven by a
combination of stellar irradiation and internal heat that powers an
outflow, which eventually depletes or entirely strips the envelope
from the rocky core \citep{Owen_Wu_2013,gupta_sculpting_2019}.
Discovering young planets and measuring their compositions and
atmospheric outflows are key steps toward testing this paradigm, which
is often invoked to explain the observed radius distribution of both
mature exoplanets \citep{Fulton_et_al_2017}, as well as younger
planets \citep{bouma_cluster_2020}.
